\texttt{davos}: a Python package ``smuggler'' for constructing lightweight reproducible notebooks

### 2022-11-01 paper/main.tex
add illustrative example fig, recompile
section 3 intro paragraph, insert ref to illustrative example fig in section 2

The \texttt{davos} config provides a simple, high-level interface for controlling various aspects of \texttt{davos}'s behavior. After importing \texttt{davos}, the \texttt{davos.config} object (a singleton) exposes a number of configurable options as attributes that can be assigned different values, checked at runtime, and displayed in the notebook cell output (see Fig.~\textcolor{red}{INSERT REF TO ILLUSTRATIVE EXAMPLE FIG} for example usage). These include:

@@

>>>>

The \texttt{davos} config provides a simple, high-level interface for controlling various aspects of \texttt{davos}'s behavior. After importing \texttt{davos}, the \texttt{davos.config} object (a singleton) exposes a number of configurable options as attributes that can be assigned different values, checked at runtime, and displayed in the notebook cell output (see Fig.~\ref{fig:illustrative-example} for example usage). These include:

@@

\begin{figure}[tp]
\centering
\includegraphics[width=\textwidth]{figs/illustrative_example}
\caption{\small \textbf{Example use case for \texttt{davos}'s functionality.}}
\label{fig:illustrative-example}
\end{figure}

Figure~\ref{fig:illustrative-example} illustrates how one might use \texttt{davos} in a real-world setting to facilitate reproducible data analyses. In this scenario, a user has acquired a dataset and pre-trained semantic model (possibly shared by a collaborator, or downloaded from a public repository) with which they want to run a set of analyses in an IPython notebook. The hypothetical dataset (a \texttt{pandas} \cite{McKi10} \texttt{DataFrame}) and model (a \texttt{scikit-learn} \cite{PedrEtal11} \texttt{Pipeline}) were created and saved using the latest versions of each package available in December 2019 and, due to their age and the formats in which they were provided, now pose certain challenges to loading and using them. The code in Figure~\ref{fig:illustrative-example} would be included at the top of the user's analysis notebook, and demonstrates how \texttt{davos} enables them to overcome these issues cleanly and efficiently, while simultaneously constructing a reproducible Python environment that ensures their analyses are always run under the same conditions, both by the user themselves and anyone with whom they share their code.
